Predictions of Occupied Beds at Faculties Providing Daily Shelter And/Or Overnight Services Using Multivariate Linear Regression Leads To Possible Maximized Efficient of Government Investment To These Faculties

### 2024-12-04 paper/paper.qmd
Finish the final part of the final paper

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Kevn Shao
thanks: "Code and data are available at: https://github.com/KevinShao1357/Toronto_Daily_Shelter_And_Overnight_Service_Modelling.git."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

# Load the necessary packages
library(tidyverse)
library(opendatatoronto)
library(janitor)
library(dplyr)
library(readr)
library(gt)
library(AER)
library(knitr)
library(kableExtra)
library(arrow)

@@

The remainder of this paper is structured as follows: @sec-data details the data and measurement process of the chosen dataset; @sec-model covers the multivariate linear regression model used in this paper; @sec-results provides results obtain from the derived model; and @sec-discussion includes discussions, such as implications and future steps, of our model, and how our results can in turn be furthermore improved.

@@

The dataset "Daily Shelter & Overnight Service Occupancy & Capacity" (@Dataset) was sourced from the dataset with same name found in Open Data Toronto. The paper's in-depth analysis and prelimary data analysis are all completed using the statistical programming language R (@R).

@@

Our results are summarized in

@@

# Appendix {-}

>>>>

---
title: "Predictions of Occupied Beds at Faculties Providing Daily Shelter And/Or Overnight Services Using Multivariate Linear Regression Leads To Possible Maximized Efficient of Government Investment To These Faculties"
author: 
  - Kevn Shao
thanks: "Code and data are available at: https://github.com/KevinShao1357/Toronto_Daily_Shelter_And_Overnight_Service_Modelling.git."
date: today
date-format: long
abstract: "Recently, the Canadian government expresses interest in continuous investment in government faculties providing daily shelter and/or overnight services. With the aim to evaluate the validity of predicting the occupied beds at a related faculties at a day, which can reflect the demand of such services at such locations, a multivariate linear regression model is constructed, with the city to Downtown Toronto, and the gender and age set to Mixed Adults. Five predictor variables are used, including two numerical variables, occupancy rate and capacity, and three categorical variables, including classification, service types, and program types. The final results showed a possible violation of linearity assumptions such as homoscedasticity and normality of errors, but also reflects the possibility of predicting the appropriate amount of investment to these facilities using this statistical approach."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

# Load the necessary packages
library(tidyverse)
library(opendatatoronto)
library(janitor)
library(dplyr)
library(readr)
library(knitr)
library(kableExtra)
library(arrow)
library(ggplot2)

@@

The remainder of this paper is structured as follows: @sec-data details the data and measurement process of the chosen dataset; @sec-model covers the multivariate linear regression model used in this paper; @sec-results provides results obtain from the derived model; @sec-discussion includes discussions, such as implications and future steps, of our model, and how our results can in turn be furthermore improved; @sec-appendix is about analysis of observational data and surveys, and is the appendix of this paper.

@@

The dataset "Daily Shelter & Overnight Service Occupancy & Capacity" (@Dataset) was sourced from the dataset with same name found in Open Data Toronto. The paper's in-depth analysis and prelimary data analysis are all completed using the statistical programming language R (@R). The book 'Telling Stories with Data' (@tellingstories) was also used to complete this paper.

Packages used to complete the paper and/or the scripts include ggplot2 (@ggplot2), tidyverse (@tidyverse), opendatatoronto (@opendatatoronto), janitor (@janitor), dplyr (@dplyr), readr (@readr), knitr (@knitr), kableExtra (@kableExtra), arrow (@arrow), and testthat (@testthat).

@@

Our results are summarized in @tbl-table9. Note that the response variable is not logged.

```{r}
#| label: tbl-table9
#| tbl-cap: "Coefficients of the Final Model"
#| echo: false
#| warning: false
#| message: false

# Extract coefficients and the intercept
coef <- coef(model_b)

# Create a data frame for the coefficients and intercept
coef_tbl <- data.frame(
  Coef = coef   
)

# Display the table using kable
kable(
  coef_tbl,
  col.names = c("Coefficient"),
  caption = "Coefficients and Intercept of the Multivariate Linear Regression Model"
)
```

@@

# Appendix A: Analysis of Observational Data and Surveys {#sec-appendix}

Here is just some analysis of my constructed multivariate linear regression model, as well as some of my understandings of this provided dataset.

As I have been analyzing the cleaned data all the time, I am only being in touch with a subset of the Open Data Toronto that is about daily shelter and overnight service occupancy and capacity that I have chosen. Therefore, I may have stepped into the Simpson's Paradox, which occurs "when we estimate some relationship for subsets of our data, but a different relationship when we consider the entire dataset" (@tellingstories). The Simpson Paradox is an instance of the ecological fallacy, which basically occurs when we try to conclude some characteristics of an individual based on their group. This paradox is also certain to be possible to happen on my analysis, since I only chose the city Downtown Toronto, whereas the original dataset is about information of same facilities, but for the entire Greater Toronto Area (GTA). For example, if for the current data about the city Downtown Toronto, the residual plots show a clear conical shape, showing a violation of the linearity assumption homoscedasticity (constant variance), then I would naturally try to log the response variable to adhere more to this assumption. After this approach, I follow the other typical procedures to construct a final multivariate linear regression model. Then, at this moment, if I then generalize the model for all cities in Greater Toronto Area (GTA), an issue may occur if for certain other cities, no conical shape appears in other residual plots, then there may exist a possibility that for these cities, when I log the response variable, the homoscedasticity assumption is then unexpectingly violated. If the frequency of these cities are too high, the model I constructed for the city Downtown Toronto may not be valid as a whole.

A similar paradox Berkson's paradox may also occur similarly. Berkson's paradox occurs when "we estimate some relationship based on the dataset that we have, but because the dataset is so selected, the relationship is different in a more general dataset" (@tellingstories). Take the cleaned version of my chosen dataset again, the current multivariate linear regression model is only relatively valid, and is not valid to the highest extent, due to the possible violation of the linearity assumptions of homoscedasticity and/or normality of errors. However, this may be not be the case for the entire dataset which has the scope of the entire Greater Toronto Area (GTA), so the model between the same predictor and response variables may be more valid, less valid, entirely valid, or not valid at all, depending on the key characteristics of variables of other subsets based on the scope of other cities in GTA.

Let's also analyze some information about the data collection process of the same Open Data Toronto dataset named 'Daily Shelter & Overnight Service Occupancy & Capacity'. According to the official website page of the dataset on Open Data Toronto, the updated information about shelter and overnight service programs, including the program's operator, location, classification, occupancy, and capacity, which are all "administered by TSSS(Toronto Shelter and Support Services" (@Dataset). However, we cannot make sure that the administration of TSSS is certainly free of mistakes, so some parts of the dataset may also be done with convenience sampling, which is a type of non-probability sampling when researchers collect data which are easiest to accest from their perspective. If this hypothesis holds true, then even if the entire dataset used, the model can be still not representative of all the related facilities in the Greater Toronto Area (GTA).
\newpage
